Exponential Random Graph Models with Big Networks: Maximum Pseudolikelihood Estimation and the Parametric Bootstrap

### 2017-07-25 TeX/conference_paper.tex
Relative Time ratio
Added a sentence about the relative time ratio: The ratio of boot MPLE to MCMLE goes to 0.2, meaning that the boot MPLE can be about 5 times faster

Figure \ref{comptime} demonstrates that all three networks only require two cores for the bootstrapped MPLE to outperform the computing time of the MCMLE and that the computing time can further be reduced if more computing cores are available. This figure also depicts that larger network in general require a longer computation time and will benefit more if the bootstrapped MPLE is used.\\ 

>>>>

Figure \ref{comptime} demonstrates that all three networks only require three cores for the bootstrapped MPLE to outperform the computing time of the MCMLE and that the computing time can further be reduced if more computing cores are available. If more computing cores are being used the ratio of the bootstrapped MPLE time to the MCMLE time levels off at about $0.2$, meaning that the computing time can be quintupled using the bootstrapped MPLE. This figure also depicts that larger network in general require a longer computation time and will benefit more if the bootstrapped MPLE is used.\\ 
